### 2012-12-19 inst/examples/ricker-oscillate-example.Rmd
no so very good on the oscillation data

```{r sdp-pars}
```

>>>>

```{r sdp-pars-ricker}
sigma_g <- 0.05
z_g <- function(sigma_g) rlnorm(1, 0, sigma_g) #1+(2*runif(1, 0,  1)-1)*sigma_g #
x_grid <- seq(0, 2.5 * K, length=101)
h_grid <- x_grid
profit = function(x,h) pmin(x, h)
delta <- 0.01
OptTime = 20
reward = profit(x_grid[length(x_grid)], x_grid[length(x_grid)]) + 1 / (1 - delta) ^ OptTime 
xT <- 0
```
